---
title: "Demonstrate Package"
output: pdf_document
params:
  data_config: !r rampdata::data_configuration()
---

```{r get_git, include = TRUE}
# The try-catch is here because the cluster's R image lacks git.
repo_name <- "unknown"
tryCatch({
        repo_name <- system("git config --get remote.origin.url", intern = TRUE)
}, error = function(x) {}
)

# The R on the cluster is also an older version that won't
# execute rampdata::data_configuration() in the preamble above.
# You can define it yourself, if that's the case.
params2 = list(data_config = rampdata::data_configuration())
```

From `r repo_name` on `r date()`, generated by `r Sys.info()[["effective_user"]]`.

# Overview

This notebook demonstrates the `rampdata` package.
It defines the data configuration in a header.
This data configuration can then help find data
within code.

```{r find_data}
cat(params$data_config$LOCALDATA)
```

# Local Path

The `local_path` command translates a keyword list into a path that's relative
to the data directory on your computer.
```{r show_path}
shapefile <- list(location = "uganda", stage = "input", path = "UBOS/outline.shp")
rampdata::local_path(shapefile, params$data_config)
```

```{r a_working_path}
edited_shapefile <- list(stage = "working", path = "UBOS/outline_fixed.shp",
                         project = "rampdata")
rampdata::local_path(edited_shapefile, params$data_config)
```

# Data configuration

That local path uses a configuration object that's initialized in
the metadata section of this notebook.
```{r, eval = FALSE}
params:
  data_config: !r rampdata::data_configuration()
```
When the notebook is built, R runs the `data_configuration` function
in order to find the location of the data on your machine. It reads
this configuration information from a `data.ini` file. Look at the help
for `data_configuration` for an example of the `data.ini` and what to
put in it.
